\documentclass{letter}

\usepackage{fullpage}

\begin{document}

{\bf Diversity Statement}\\
{\bf Shiyu Ji, applying Computer Science PhD}\\
\rule{\textwidth}{1pt}

The most important reason that drives me to pursue a graduate degree is my strong interest in research. I became interested in cryptography and related math backgrounds when I was a junior, and I did some image encryption research in Harbin Institute of Technology. After I obtained my bachelor degree, I went to Oklahoma State University (OSU) to continue my computer science research, and my research interests expanded to wireless networks and crowdsensing. During the concrete research work in OSU, I found that in order to understand essentially, one has to learn related materials comprehensively. That is, it is necessary to sufficiently practice on some advanced topics, i.e., computational complexity, computer vision, category theory, etc. On the other hand, it is extremely helpful to speak with other scholars, since one might have misunderstandings on the materials in the textbooks or papers, or one might not think about a particular topic very deeply. Communicating with others may help avoid such traps. Purdue is a very good platform for the top scholars on the earth to share the ideas.

I am also very interested in teaching, and I became a teaching assistant in OSU. When I prepared the course materials, I came to find that I have not thought about the topics deeply enough before. The instructor Dr. HK Dai told me that to aim higher, one needs some advanced academical training, i.e., by attending a prestigious graduate school. The computer science program in Purdue is a pretty good choice for me. When I attended INFOCOM 2014, the committee chair Dr. Yuguang Fang also encouraged me to apply the top graduate colleges in the US. It is obvious that high quality academical training will be extraordinarily beneficial for me.

My ultimate goal is to earn a decent position in academia, i.e., a professor in a top university. To get well prepared for the challenging future, I think Purdue is the best place for me.

Shiyu Ji, Graduate Student,\\
Department of Computer Science\\
Oklahoma State University\\
shiyu@cs.okstate.edu\\
\today{}
\end{document}