\documentclass{article}

\usepackage{setspace}
\usepackage{fullpage}

\begin{document}

\setlength{\parindent}{0cm}
\setlength{\parskip}{\baselineskip}
\pagestyle{empty}

To Whom It May Concern,

I am writing to apply for the US National Science Foundation (NSF) travel grant opportunity for US-based students (Type B) for INFOCOM 2014. I have the paper \emph{DAWN: Defending Against Wormhole Attacks in Wireless Network Coding Systems} accepted by INFOCOM 2014.

I am a second year PhD candidate at Oklahoma State University, working on incentive issues, data privacy and cyber security of crowdsourcing and wireless networks.

I have been working on the incentive mechanisms of crowdsourcing. I have investigated the problems on crowdsourcing such as \emph{Sensing Uncertainty} and \emph{Finite Sensing Precisions}. I have proposed different mechanisms that can achieve equilibria for various scenarios. I have also studied the privacy preserving mechanisms in crowdsourcing that can achieve k-anonymity and differential privacy. For the cyber security in wireless networks, I have researched the wormhole attack in network coding systems, and participated in designing the algorithms to defend against wormhole attacks.

I have authored/coauthored 4 papers. 3 have been published or accepted by prestigious conferences and journals like INFOCOM, ICC and Journal of Electronic Imaging.

By attending the prestigious conferences like INFOCOM, I can gain abundant advanced knowledge from the face-to-face discussions with the active contributors in my research field. Getting to know the people in the same field can definitely help me prepare the academic career in the future.

Thank you.

Shiyu Ji, PhD Candidate,\\
Department of Computer Science\\
Oklahoma State University\\
shiyu@cs.okstate.edu\\
\today{}
\end{document}